---
title: "ShinyApp"
author: "Jenny Biechele-Speziale"
date: "6/16/2020"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Making Basic Models for Swiss Fertility Data
This presentation is about making simple models for the swiss data set. The two model options include a basic linear regression using R's lm() function, and a locally estimated scatterplot smoothing regression (or loess) using R's loess() function. 

The application allows for the user to select the desired predictor (only one predictor can be chosen) and model type (either loess or basic linear regression).

The user can also select the confidence bounds for the model they select.

This tool gives an interactive introduction to basic model fitting. 


## Plotting Swiss Fertility Data With Various Models:

```{r eruptions}
library(ggplot2)
shinyApp(
  ui=fluidPage(
    sidebarLayout(
        sidebarPanel(
            radioButtons("p", "Select a Variable:",                    
                         list("Agriculture"='Agriculture', "Examination"='Examination', "Education"='Education', "Catholic"='Catholic', "Infant Mortality"='Infant Mortality')),  
            radioButtons("q","Select a Model Method:",
                         list("Basic Linear Model"="lm","Loess"="loess")),
            sliderInput("slider","Adjust the confidence bounds!",
                        min=0,
                        max=1,
                        value=0.95)
        ),
        mainPanel(
            h4(textOutput("model")),
            plotOutput("distPlot")
        ) 
    )
    ),

# Define server logic required to draw a histogram
server=function(input,output){
  output$distPlot <- renderPlot({
    if(input$p=='Agriculture'){    
      i<-2     }
    if(input$p=='Examination'){
      i<-3     }
    if(input$p=='Education'){
      i<-4     }
    if(input$p=='Catholic'){
      i<-5     }
    if(input$p=='Infant Mortality'){
      i<-6     }
    x <- swiss[,i]
    df<-data.frame(swiss$Fertility,x)
    ggplot(data=df,aes(x,swiss.Fertility))+
      geom_smooth(aes(),method=input$q,level=input$slider)+
      geom_point()+
      xlab(input$p)+
      ylim(c(25,range(swiss$Fertility)[2]))+
      xlim(range(x))+
      ylab("Fertility")
  })
  dataInput<-reactive({
    if(input$q=="Basic Linear Model"){
      fit<-lm(swiss.Fertility~y,df)
    }
    if(input$q=="Loess"){
      fit<-loess(swiss.Fertility~y,df)
    }
  })
  output$model<-renderText({
    paste("You have selected a ", input$q, "model, comparing Fertility vs. ", input$p)
  })
})
```


## About the Data
<font size="4">This data comes from the <b>Swiss Fertility and Socioeconomic Indicators (1888) Data</b>. This dataset offers a standardized fertility measure and socio-economic indicators for each of the 47 provinces of Switzerland in the 1888. The socio-economic indicators include:</font>

<font size="4">Agriculture</font>

:     <font size="3">Percent of males involved in agriculture as occupation</font>

<font size="4">Examination</font>

:    <font size="3">Percent of draftees receiving highest mark on army examination</font>
  
<font size="4">Education</font>

:   <font size="3">Percent of education beyond primary school for draftees</font>

<font size="4">Catholic</font>

:   <font size="3">Percent of ‘catholic’ respondants (as opposed to ‘protestant’)</font>

<font size="4">Infant Mortality</font>

:   <font size="3">Live births who live less than 1 year</font>

## Thank you!

<font size="4">Check out [my github](https://github.com/ander689) for more tutorials!</font>

Data Source:

<font size="3"><i>Project “16P5”, pages 549–551 in</i>

<i>Mosteller, F. and Tukey, J. W. (1977) Data Analysis and Regression: A Second Course in Statistics. Addison-Wesley, Reading Mass.</i>


https://opr.princeton.edu/archive/pefp/switz.aspx</font>



